% filepath: src/sections/04_outcomes.tex

\section{Expected Outcomes and Challenges}

\begin{frame}{Anticipated Research Outcomes}
    \begin{columns}[T]
        \column{0.55\textwidth}
        \begin{itemize}
            \item \textbf{Search Space Optimization} \\
            {\footnotesize \faArrowDown \quad Significant reduction in nodes visited vs. Baseline Algorithm.}
            \vfill
            \item \textbf{Constraint Satisfaction} \\
            {\footnotesize \faCheckSquareO \quad 100\% hard-constraint feasibility with optimized soft-preference scoring.}
            \vfill
            \item \textbf{Framework Adaptability} \\
            {\footnotesize \faCogs \quad Empirical validation of the Python/JS prototype across diverse curricula.}
        \end{itemize}
        
        \column{0.45\textwidth}
        \centering
        \vspace{0.5cm}
        \begin{tikzpicture}[scale=0.85]
            \draw[->, thick] (0,0) -- (3.5,0) node[right] {\tiny Input Size};
            \draw[->, thick] (0,0) -- (0,3.5) node[above] {\tiny Search Space};
            
            \draw[gray, dashed, thick] (0.2,0.2) .. controls (1.5,0.5) and (2.2,1.2) .. (3.2,3.2);
            \node[gray, right] at (3.2,3.2) {\tiny Baseline};
            
            \draw[SecondaryColor, ultra thick] (0.2,0.2) .. controls (1.2,0.8) and (2.2,1.0) .. (3.2,1.2);
            \node[SecondaryColor, right] at (3.2,1.2) {\tiny DRL};
            
            \filldraw[AlertColor] (3.2,1.2) circle (2pt);
        \end{tikzpicture}
        
        \vspace{0.2cm}
        {\scriptsize Fig: Projected Heuristic Efficacy}
    \end{columns}
\end{frame}

\begin{frame}{Challenges and Future Work}
    \begin{alertblock}{Current Technical Challenges}
        \begin{itemize}
            \item \textbf{Computational Overhead:} Balancing DRL inference time against the actual time saved during tree pruning.
            \item \textbf{Data Scarcity:} Obtaining high-fidelity student preference data for cross-institutional testing.
        \end{itemize}
    \end{alertblock}

    \vspace{0.3cm}

    \begin{alertblock}{Future Horizons}
        \begin{itemize}
            \item \textbf{Generalization:} Testing the agent on vastly different curriculum structures (e.g., UNI Lima vs. UNICAMP).
            \item \textbf{Explainability:} Implementing XAI methods to verify agent pruning logic.
        \end{itemize}
    \end{alertblock}
    
    \vfill
    \centering
    \footnotesize \textit{Focus: Transitioning from a Prototype to a Scalable Academic Tool.}
\end{frame}
